Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-04-17 paper/paper.tex
We've room for another heading
Fix weird hyphenation

\subsection{Why is the Central Region Hard?}

@@

@@

The model we have proposed may be extended to graphs with labels on the vertices or edges, which
arise naturally in many applications. Broadly speaking, randomly allocated labels make the problem
easier by restricting the search space, although there are pathological cases where increasing the
number of labels shifts an instance from the easy satisfiable region to being close to the phase
transition. The model may also be extended to the (decision version of the) maximum common subgraph
problem. The reduction to maximum clique is a competitive approach for the maximum common subgraph
problem, so it is interesting to observe that some of the easy portions of the search space become
hard under this reduction---this suggests a possible unnecessary weakness of maximum clique
algorithms on certain kinds of input. (Maximum clique algorithms use a greedy colouring as a bound,
and the association graphs produced by this reduction can be very bad for greedy colourings in the
same way that crown graphs are.)

>>>>

\subsection{Is the Central Region Genuinely Hard?}

@@

\subsection{Constrainedness}

@@

The model we have proposed may be extended to graphs with labels on the vertices or edges, which
arise naturally in many applications. Broadly speaking, randomly allocated labels make the problem
easier by restricting the search space, although there are pathological cases where increasing the
number of labels shifts an instance from the easy satisfiable region to being close to the phase
transition. The model may also be extended to the (decision version of the) maximum common subgraph
problem. The maximum clique approach is competitive for the maximum common subgraph problem, so it
is interesting to observe that some of the easy portions of the search space become hard under this
reduction---this suggests a possible unnecessary weakness of maximum clique algorithms on certain
kinds of input. (Maximum clique algorithms use a greedy colouring as a bound, and the association
graphs produced by this reduction can be very bad for greedy colourings in the same way that crown
graphs are.)
